% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
]{article}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdftitle={Alina Christenbury's CV},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering

\title{Alina Christenbury's CV}
\date{}

\begin{document}
\maketitle

\hypertarget{alina-christenbury}{%
\section{Alina Christenbury}\label{alina-christenbury}}

Spatial Games Researcher.

302.648.2117 \textbar{}
\href{https://github.com/AlinaWithAFace/alinawithaface.github.io/tree/2022bba30520ae159c38e17b2361bdefa4bb71d4/alinac@udel.edu}{alinac@udel.edu}
\textbar{} \href{http://alinac.me}{alinac.me}

\hypertarget{research-interests}{%
\subsection{Research Interests}\label{research-interests}}

Games, collaborative experiences, XR technology, human-computer
interaction, machine learning applications in games, generative art,
procedural generation

\hypertarget{education}{%
\subsection{Education}\label{education}}

\texttt{June\ 2019\ —\ Present} \textbf{Computer Science PhD.}
University of Delaware, Newark, DE.

\texttt{Aug\ 2015\ —\ May\ 2019} \textbf{Computer Science B.S.}
University of Delaware, Newark, DE. 3.28/4.0.

\hypertarget{awards}{%
\subsection{Awards}\label{awards}}

\texttt{May\ 2019}
\href{https://grad.udel.edu/fees-and-funding/unidel-grad-scholars-award/}{Unidel
Distinguished Graduate Scholars Program}

\texttt{May\ 2019} Lauri Pfeffer Shinn Memorial Award

\texttt{Dec\ 2018} \href{https://glitch.mn/powerleveling/}{GLITCH's
Power Leveling Program}

\texttt{Fall\ 2018,\ Spring\ 2018,\ Spring\ 2016,\ Fall\ 2015} Dean's
List

\hypertarget{experience}{%
\subsection{Experience}\label{experience}}

\texttt{May\ 2019\ —\ Present} \textbf{Founder.} Delaware Games
Collective. Newark, DE.

\texttt{Sep\ 2018\ —\ October\ 2019} \textbf{VIP:VR Project Manager.}
University of Delaware. Newark, DE.

\begin{itemize}
\tightlist
\item
  Project goals include exploring the applications of virtual reality in
  commercial and educational projects.
\item
  Led a team of undergraduates in designing and creating a cooperative
  virtual reality gameplay experience.
\end{itemize}

\texttt{Jun\ 2018\ —\ Aug\ 2018} \textbf{Virtual Reality Summer
Scholar.} University of Delaware. Newark, DE.

\begin{itemize}
\tightlist
\item
  Conducted research with university faculty centered around virtual
  reality and augmented reality in order to prepare for an undergraduate
  research project. Experimented with gesture-based gameplay and
  interaction in virtual environments using a Leap Motion hand tracking
  module.
\item
  Constructed an augmented reality headset prototype using 3D printed
  and machined parts.
\end{itemize}

\texttt{Jan\ 2018\ —\ Feb\ 2018} \textbf{Front End Developer.} Golden
Egg Labs. Newark, DE.

\begin{itemize}
\tightlist
\item
  Led re-styling and refactoring of a web app user interface.
\item
  Introduced SASS and other frameworks to a CSS-based product line
  enabling variable styling for multiple clients.
\end{itemize}

\texttt{May\ 2017\ —\ Aug\ 2017} \textbf{Game Development Intern.}
University of Delaware. Newark, DE.

\begin{itemize}
\tightlist
\item
  Collaborated on a team to develop an educational game aimed at 9-10
  year old children to be installed in the Delaware Department of
  Natural Resource and Environmental Control lobby.
\end{itemize}

\texttt{Feb\ 2017\ —\ May\ 2017} \textbf{Game Design Intern.} SmartyPal.
Philadelphia, PA.

\begin{itemize}
\tightlist
\item
  Prototyped various minigames built in Unity based on learning and
  education.
\item
  Researched and drafted reports on competition in the target market.
\item
  Collected feedback and user testing results on applications
\item
  Assisted in creating promotional materials, such as videos and
  presentations
\end{itemize}

\hypertarget{hackathons}{%
\subsection{Hackathons}\label{hackathons}}

\texttt{Jan\ 2019}
\href{https://realityvirtuallyhack.com/}{\textbf{Reality Virtually
Hackathon}}\textbf{.} MIT Media Lab. Cambridge, MA.

\texttt{Dec\ 2019} \textbf{HenHacks.} University of Delaware. Newark,
DE.

\texttt{Nov\ 2018} \href{https://hackprinceton.com/}{\textbf{Hack
Princeton}}\textbf{.} Princeton University. Princeton, NJ.

\texttt{Jan\ 2018}
\href{http://www.hoyahacks.com/}{\textbf{HoyaHacks}}\textbf{.}
Georgetown University. Washington, DC.

\texttt{Apr\ 2018} \textbf{Delhack.} University of Delaware. Newark, DE.

\texttt{Jun\ 2016}
\href{https://www.hackathon.com/event/dataworks—delawares-first-open-data-hackathon-24040563974}{\textbf{Dataworks:
Delaware's First Open Data Hackathon}}\textbf{.} Open Data Delaware.
Wilmington DE.

\hypertarget{research-experience}{%
\subsection{Research Experience}\label{research-experience}}

\texttt{Jun\ 2018\ —\ Aug\ 2018} \textbf{Summer Scholars Undergraduate
Research Program.} University of Delaware.

\hypertarget{invited-talks}{%
\subsection{Invited Talks}\label{invited-talks}}

\texttt{Jan\ 2019}
\href{https://www.ted.com/tedx/events/32155}{\textbf{A Flick of the
Wrist: Defining the Next Generation of Human-Computer
Interaction}}\textbf{.} TEDx Goldey Beacom College Salon

\hypertarget{panels}{%
\subsection{Panels}\label{panels}}

\texttt{Oct\ 2018} \textbf{Are you interested in Virtual Reality?}
Rewriting the Code. Webinar.

\hypertarget{poster-presentations}{%
\subsection{Poster Presentations}\label{poster-presentations}}

\texttt{Oct\ 2018}
\href{https://www.cis.udel.edu/55th-anniversary-celebration/}{\textbf{Computer
Science 55th Anniversary Celebration}}\textbf{.} University of Delaware.

\texttt{Aug\ 2018} \textbf{Undergraduate Research and Service Scholar
Celebratory Symposium.} University of Delaware.

\hypertarget{press}{%
\subsection{Press}\label{press}}

\texttt{Aug\ 2018}
\href{https://www.udel.edu/udaily/2018/august/alina-christenbury-virtual-reality-summer-research/}{\textbf{Seeing
the World Through a Different Lens}}. UDaily. Interview by Tracey
Bryant.

\hypertarget{technical-skills}{%
\subsection{Technical Skills}\label{technical-skills}}

\hypertarget{game-engines}{%
\subsubsection{Game Engines}\label{game-engines}}

Unity

\hypertarget{programming-languages}{%
\subsubsection{Programming Languages}\label{programming-languages}}

C\#, Java, C/C++, Python, LaTeX

\hypertarget{web}{%
\subsubsection{Web}\label{web}}

HTML, CSS, SCSS, Javascript, React, Markdown

\hypertarget{ides}{%
\subsubsection{IDEs}\label{ides}}

IntelliJ IDEA, CLion, Webstorm

\hypertarget{version-control}{%
\subsubsection{Version Control}\label{version-control}}

Git, Sourcetree

\hypertarget{film}{%
\subsubsection{Film}\label{film}}

Final Cut Pro 10, Adobe After Effects

\hypertarget{coursework}{%
\subsection{Coursework}\label{coursework}}

\texttt{Fall\ 2018} Human-Computer Interaction

\hypertarget{extracurriculars}{%
\subsection{Extracurriculars}\label{extracurriculars}}

\texttt{May\ 2018\ —\ Jan\ 2019} \textbf{President.} Association for
Computing Machinery at the University of Delaware

\begin{itemize}
\tightlist
\item
  Led weekly coding challenges, coordinated hackathons
\end{itemize}

\texttt{May\ 2017\ —\ May\ 2018} \textbf{Vice President.} Casual Video
Game Club at the University of Delaware.

\begin{itemize}
\tightlist
\item
  Concentrated university gaming community onto a single communication
  platform
\end{itemize}

\texttt{May\ 2017\ —\ May\ 2018} \textbf{Treasurer.} Humans vs Zombies
at the University of Delaware.

\begin{itemize}
\tightlist
\item
  Managed club inventory and assets acquisition, assisted in planning
  events
\end{itemize}

\textbf{Freelance Web Developer}

\begin{itemize}
\tightlist
\item
  \href{https://github.com/AlinaWithAFace/alinawithaface.github.io/tree/1a9d04fc69b3ad64623cd7951e076f77f9a0135b/axeng.com}{Axiom
  Engineering}
\item
  \href{http://www.johnsitaliandeli.com/}{John's Italian Deli}
\end{itemize}

\hypertarget{personal}{%
\subsection{Personal}\label{personal}}

Twitter: {[}@AlinaWithAFace{]}(https://twitter.com/AlinaWithAFace)

\end{document}
